### 2012-07-09 talk/ecoop2009/rainbow.tex
fix few XXXs
update year

From a partial evaluation point of view, promotion is the converse of
the operation generally known as \emph{lift} \cite{XXX}.  Lifting a value means
copying a variable whose binding time is compile-time into a variable
whose binding time is run-time – it corresponds to the compiler
``forgetting'' a particular value that it knew about.  By contrast,
promotion is a way for the compiler to gain \emph{more} information about
the run-time execution of a program. Clearly, this requires
fine-grained feedback from run-time to compile-time, thus a
dynamic setting.

@@

If later an instance of \lstinline{IntObj} hits the flexswitch again, the
code is executed without needing of more calls to the JIT compiler.  On the
other hand, if the flexswitch is hit by an instance of some other class, the
\lstinline{default} branch will be selected again and the whole process will
restart.

>>>>

From a partial evaluation point of view, promotion is the converse of
the operation generally known as \emph{lift}.  Lifting a value means
copying a variable whose binding time is compile-time into a variable
whose binding time is run-time – it corresponds to the compiler
``forgetting'' a particular value that it knew about.  By contrast,
promotion is a way for the compiler to gain \emph{more} information about
the run-time execution of a program. Clearly, this requires
fine-grained feedback from run-time to compile-time, thus a
dynamic setting.

@@

If later an instance of \lstinline{IntObj} hits the flexswitch again, the
code is executed without needing more calls to the JIT compiler.  On the
other hand, if the flexswitch is hit by an instance of some other class, the
\lstinline{default} branch will be selected again and the whole process will
restart.
